\subsubsection*{\texttt{22-index-sentences-default}}
\label{app:samples:22_index_sentences_default}

\paragraph{Q3: How long does the Haste spell last?}
\noindent \textbf{Corr.:}~4.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} With a 3rd-level spell slot, the Haste spell lasts for concentration, up to 1 minute.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Spells/Haste} -- \#\#\# Haste  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 30 \ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Spells/Modify Memory} -- \#\#\# Modify Memory  *5th-level enchantment*  **Casting Time:** 1 action  **Range:\ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Treasure/Tome of Understanding} -- \#\#\# Tome of Understanding  *Wondrous item, very rare*  This book contains intuit\ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Spells/Geas} -- \#\#\# Geas  *5th-level enchantment*  **Casting Time:** 1 minute  **Range:** 60 fee\ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Spells/Divination} -- \#\#\# Divination  *4th-level divination (ritual)*  **Casting Time:** 1 action  **R\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q5: Can a grappled creature cast spells?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.12\\

\noindent\textbf{Antwort:} The provided rules do not specify if a grappled creature is able to cast spells or not while in that condition.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Spells/# Spellcasting} -- \# SPELLCASTING  Magic permeates fantasy gaming worlds and often appears in the f\ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Spells/# Spellcasting} -- > >**Illusion** spells deceive the senses or minds of others. They cause people \ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Monsters/# Monster Statistics} -- An innate spell can have special rules or restrictions. For example, a drow mage\ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Spells/# Spellcasting} -- To cast a spell as a ritual, a spellcaster must have a feature that grants the a\ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Gameplay/Combat} -- \# Actions in Combat  When you take your action on your turn, you can take one of\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q12: If a creature has exhaustion level 3 and is also restrained, what is its movement speed?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} A creature with exhaustion level 3 has its speed halved. The restrained condition does not directly affect the creature's movement speed. Thus, the creature's movement speed would be half its base speed.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Gamemastering/Conditions} -- If an already exhausted creature suffers another effect that causes exhaustion, \ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Gameplay/Adventuring} -- \#\# Speed  Every character and monster has a speed, which is the distance in feet\ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Gamemastering/Conditions} -- \#\# Petrified  - A petrified creature is transformed, along with any nonmagical o\ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Spells/Slow} -- \#\#\# Slow  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 120 \ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Monsters/# Monster Statistics} -- \#\#\# Climb  A monster that has a climbing speed can use all or part of its moveme\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q16: Can you use Action Surge to cast two leveled spells in one turn?}
\noindent \textbf{Corr.:}~3.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.00\\

\noindent\textbf{Antwort:} Yes, if you and I, who aren't incapacitated, have an Action Surge, we can each use it to cast two leveled spells during the same turn. However, the context does not provide enough information to determine if there are any restrictions on the number or level of those spells for the Ranger class.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Classes/Wizard} -- \#\#\#\# Empowered Evocation  Beginning at 10th level, you can add your Intelligence\ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Characterizations/Multiclassing} -- ***Spells Known and Prepared***. You determine what spells you know and can prep\ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Gameplay/Combat} -- \# Actions in Combat  When you take your action on your turn, you can take one of\ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Classes/Sorcerer} -- \#\#\# Font of Magic  At 2nd level, you tap into a deep wellspring of magic within \ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Classes/Sorcerer} -- You can use only one Metamagic option on a spell when you cast it, unless otherw\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}
