\subsubsection*{\texttt{32-retrieval-fusion-3q}}
\label{app:samples:32_retrieval_fusion_3q}

\paragraph{Q3: How long does the Haste spell last?}
\noindent \textbf{Corr.:}~5.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} The Haste spell lasts for a duration of concentration, up to 1 minute.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0500]} \textit{Spells/Haste} -- \#\#\# Haste  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 30 \ldots
  \item[\textbf{\#2}] \texttt{[0.0328]} \textit{Spells/# Spellcasting} -- \#\# Duration  A spell's duration is the length of time the spell persists. A dura\ldots
  \item[\textbf{\#3}] \texttt{[0.0318]} \textit{Spells/Slow} -- \#\#\# Slow  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 120 \ldots
  \item[\textbf{\#4}] \texttt{[0.0317]} \textit{Spells/Geas} -- \#\#\# Geas  *5th-level enchantment*  **Casting Time:** 1 minute  **Range:** 60 fee\ldots
  \item[\textbf{\#5}] \texttt{[0.0313]} \textit{Classes/Sorcerer} -- \#\#\#\# Extended Spell  When you cast a spell that has a duration of 1 minute or lo\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q5: Can a grappled creature cast spells?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} I cannot find this in the provided rules if a grappled creature is able to cast spells or not. The context only mentions that spellcasters can cast spells during combat and that some spells have a melee component, but it does not specify any restrictions on casting spells based on being grappled.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0490]} \textit{Gameplay/Combat} -- \#\# Cast a Spell  Spellcasters such as wizards and clerics, as well as many monst\ldots
  \item[\textbf{\#2}] \texttt{[0.0489]} \textit{Gameplay/Combat} -- \#\#\# Grappling  When you want to grab a creature or wrestle with it, you can use \ldots
  \item[\textbf{\#3}] \texttt{[0.0476]} \textit{Gamemastering/Conditions} -- \#\# Grappled  - A grappled creature's speed becomes 0, and it can't benefit from \ldots
  \item[\textbf{\#4}] \texttt{[0.0474]} \textit{Monsters/# Monster Statistics} -- \#\#\# Innate Spellcasting  A monster with the innate ability to cast spells has th\ldots
  \item[\textbf{\#5}] \texttt{[0.0469]} \textit{Spells/Arcane Hand} -- ***Grasping Hand***. The hand attempts to grapple a Huge or smaller creature wit\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q12: If a creature has exhaustion level 3 and is also restrained, what is its movement speed?}
\noindent \textbf{Corr.:}~3.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.75\\

\noindent\textbf{Antwort:} The context provided does not give enough information to determine the movement speed of a creature with exhaustion level 3 and also restrained. The rules for exhaustion state that it has no effect on a creature's movement speed, but the rules for being restrained state that the creature's movement \ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0500]} \textit{Gamemastering/Conditions} -- \#\# Restrained  - A restrained creature's speed becomes 0, and it can't benefit f\ldots
  \item[\textbf{\#2}] \texttt{[0.0479]} \textit{Gamemastering/Conditions} -- \#\# Exhaustion  Some special abilities and environmental hazards, such as starvat\ldots
  \item[\textbf{\#3}] \texttt{[0.0460]} \textit{Monsters/Lion (Creature)} -- \#\#\# Lion  *Large beast, unaligned*  **Armor Class** 12  **Hit Points** 26 (4d10+\ldots
  \item[\textbf{\#4}] \texttt{[0.0318]} \textit{Monsters/Bat (Creature)} -- \#\#\# Bat  *Tiny beast, unaligned*  **Armor Class** 12  **Hit Points** 1 (1d4-1)  \ldots
  \item[\textbf{\#5}] \texttt{[0.0315]} \textit{Gamemastering/Conditions} -- \#\# Unconscious  - An unconscious creature is incapacitated (see the condition), \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q16: Can you use Action Surge to cast two leveled spells in one turn?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} I cannot find this in the provided rules that you can use Action Surge to cast two leveled spells in one turn. Action Surge only allows you to take an additional action on top of your regular action and a possible bonus action. Casting a spell is considered an action, so you can only cast one spell \ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0497]} \textit{Classes/Fighter} -- \#\#\# Action Surge  Starting at 2nd level, you can push yourself beyond your norma\ldots
  \item[\textbf{\#2}] \texttt{[0.0481]} \textit{Characterizations/Multiclassing} -- If you have more than one spellcasting class, this table might give you spell sl\ldots
  \item[\textbf{\#3}] \texttt{[0.0474]} \textit{Spells/# Spellcasting} -- \#\#\# Bonus Action  A spell cast with a bonus action is especially swift. You must\ldots
  \item[\textbf{\#4}] \texttt{[0.0314]} \textit{Spells/Confusion} -- \#\#\# Confusion  *4th-level enchantment*  **Casting Time:** 1 action  **Range:** 9\ldots
  \item[\textbf{\#5}] \texttt{[0.0311]} \textit{Classes/Sorcerer} -- \#\#\#\# Quickened Spell  When you cast a spell that has a casting time of 1 action,\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}
