\subsubsection*{\texttt{33-retrieval-bm25-fusion}}
\label{app:samples:33_retrieval_bm25_fusion}

\paragraph{Q3: How long does the Haste spell last?}
\noindent \textbf{Corr.:}~5.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} The Haste spell lasts for a duration of concentration, up to 1 minute. (From the provided context)

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0667]} \textit{Spells/Haste} -- \#\#\# Haste  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 30 \ldots
  \item[\textbf{\#2}] \texttt{[0.0469]} \textit{Spells/Modify Memory} -- \#\#\# Modify Memory  *5th-level enchantment*  **Casting Time:** 1 action  **Range:\ldots
  \item[\textbf{\#3}] \texttt{[0.0328]} \textit{Spells/# Spellcasting} -- \#\# Duration  A spell's duration is the length of time the spell persists. A dura\ldots
  \item[\textbf{\#4}] \texttt{[0.0317]} \textit{Spells/Geas} -- \#\#\# Geas  *5th-level enchantment*  **Casting Time:** 1 minute  **Range:** 60 fee\ldots
  \item[\textbf{\#5}] \texttt{[0.0313]} \textit{Spells/## Spell Lists} -- \#\#\#\# 3rd Level  - Blink - Clairvoyance - Counterspell - Daylight - Dispel Magic \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q5: Can a grappled creature cast spells?}
\noindent \textbf{Corr.:}~1.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} I cannot find this in the provided rules whether a grappled creature can cast spells or not. The context only discusses grappling rules and the Sorcerer's Metamagic ability called "Careful Spell."

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0653]} \textit{Gameplay/Combat} -- \#\#\# Grappling  When you want to grab a creature or wrestle with it, you can use \ldots
  \item[\textbf{\#2}] \texttt{[0.0640]} \textit{Spells/Arcane Hand} -- ***Grasping Hand***. The hand attempts to grapple a Huge or smaller creature wit\ldots
  \item[\textbf{\#3}] \texttt{[0.0631]} \textit{Gamemastering/Conditions} -- \#\# Grappled  - A grappled creature's speed becomes 0, and it can't benefit from \ldots
  \item[\textbf{\#4}] \texttt{[0.0333]} \textit{Gameplay/Combat} -- \#\# Cast a Spell  Spellcasters such as wizards and clerics, as well as many monst\ldots
  \item[\textbf{\#5}] \texttt{[0.0315]} \textit{Monsters/# Monster Statistics} -- \#\#\# Innate Spellcasting  A monster with the innate ability to cast spells has th\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q12: If a creature has exhaustion level 3 and is also restrained, what is its movement speed?}
\noindent \textbf{Corr.:}~4.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.75\\

\noindent\textbf{Antwort:} The context provided does not give enough information to determine the movement speed of a creature with exhaustion level 3 and also restrained. The rules for exhaustion only mention that a creature's speed is reduced by 5 feet for each level of exhaustion (up to a maximum of 20 feet at level 5). Ho\ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0656]} \textit{Gamemastering/Conditions} -- \#\# Restrained  - A restrained creature's speed becomes 0, and it can't benefit f\ldots
  \item[\textbf{\#2}] \texttt{[0.0651]} \textit{Gamemastering/Conditions} -- \#\# Exhaustion  Some special abilities and environmental hazards, such as starvat\ldots
  \item[\textbf{\#3}] \texttt{[0.0481]} \textit{Spells/Freedom of Movement} -- \#\#\# Freedom of Movement  *4th-level abjuration*  **Casting Time:** 1 action  **R\ldots
  \item[\textbf{\#4}] \texttt{[0.0312]} \textit{Monsters/Wraith} -- \#\# Wraith  *Medium undead, neutral evil*  **Armor Class** 13  **Hit Points** 67 \ldots
  \item[\textbf{\#5}] \texttt{[0.0311]} \textit{Monsters/Ghost} -- \#\# Ghost  *Medium undead, any alignment*  **Armor Class** 11  **Hit Points** 45 \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q16: Can you use Action Surge to cast two leveled spells in one turn?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} I cannot find this in the provided rules that you can use Action Surge to cast two leveled spells in one turn. Action Surge only allows you to take one additional action on top of your regular action and a possible bonus action. Casting a spell is considered an action. Therefore, you can only cast o\ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0661]} \textit{Classes/Fighter} -- \#\#\# Action Surge  Starting at 2nd level, you can push yourself beyond your norma\ldots
  \item[\textbf{\#2}] \texttt{[0.0331]} \textit{Classes/Fighter} -- **Table- The Fighter**  | Level | Proficiency Bonus | Features                  \ldots
  \item[\textbf{\#3}] \texttt{[0.0323]} \textit{Spells/Heal} -- \#\#\# Heal  *6th-level evocation*  **Casting Time:** 1 action  **Range:** 60 feet \ldots
  \item[\textbf{\#4}] \texttt{[0.0315]} \textit{Spells/# Spellcasting} -- \#\#\# Bonus Action  A spell cast with a bonus action is especially swift. You must\ldots
  \item[\textbf{\#5}] \texttt{[0.0315]} \textit{Spells/Create Undead} -- \#\#\# Create Undead  *6th-level necromancy*  **Casting Time:** 1 minute  **Range:*\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}
