\subsubsection*{\texttt{40-post-rerank}}
\label{app:samples:40_post_rerank}

\paragraph{Q3: How long does the Haste spell last?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} With concentration from the caster, the Haste spell lasts for up to 1 minute. At higher levels, the duration is extended: 1 year with a 7th or 8th level spell slot, and indefinitely with a 9th level spell slot until ended by a specific spell.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[-1.1630]} \textit{Spells/Haste} -- \#\#\# Haste  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 30 \ldots
  \item[\textbf{\#2}] \texttt{[-4.2668]} \textit{Spells/Modify Memory} -- \#\#\# Modify Memory  *5th-level enchantment*  **Casting Time:** 1 action  **Range:\ldots
  \item[\textbf{\#3}] \texttt{[-4.3387]} \textit{Spells/Bestow Curse} -- \#\#\# Bestow Curse  *3rd-level necromancy*  **Casting Time:** 1 action  **Range:**\ldots
  \item[\textbf{\#4}] \texttt{[-4.3627]} \textit{Spells/# Spellcasting} -- \#\# Duration  A spell's duration is the length of time the spell persists. A dura\ldots
  \item[\textbf{\#5}] \texttt{[-4.8813]} \textit{Spells/Geas} -- \#\#\# Geas  *5th-level enchantment*  **Casting Time:** 1 minute  **Range:** 60 fee\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q5: Can a grappled creature cast spells?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} I cannot find this in the provided rules if a grappled creature is able to cast spells or not. The rules only mention that a grappled creature can make a Wisdom saving throw at the end of each of its turns to end the effect of the Arcane Hand spell.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[2.1648]} \textit{Spells/Arcane Hand} -- ***Grasping Hand***. The hand attempts to grapple a Huge or smaller creature wit\ldots
  \item[\textbf{\#2}] \texttt{[0.5121]} \textit{Gamemastering/Conditions} -- \#\# Grappled  - A grappled creature's speed becomes 0, and it can't benefit from \ldots
  \item[\textbf{\#3}] \texttt{[-1.5698]} \textit{Gameplay/Combat} -- \#\#\# Grappling  When you want to grab a creature or wrestle with it, you can use \ldots
  \item[\textbf{\#4}] \texttt{[-3.3439]} \textit{Spells/# Spellcasting} -- \# Rituals  Certain spells have a special tag: ritual. Such a spell can be cast f\ldots
  \item[\textbf{\#5}] \texttt{[-4.5285]} \textit{Spells/Confusion} -- \#\#\# Confusion  *4th-level enchantment*  **Casting Time:** 1 action  **Range:** 9\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q12: If a creature has exhaustion level 3 and is also restrained, what is its movement speed?}
\noindent \textbf{Corr.:}~1.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.88\\

\noindent\textbf{Antwort:} The context provided does not give information about the movement speed of a creature with exhaustion level 3 and also restrained. The context only mentions that exhaustion is a condition with six levels and provides a table of effects for each level. It also mentions a spell called "Dominate Person\ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.5239]} \textit{Gamemastering/Conditions} -- \#\# Exhaustion  Some special abilities and environmental hazards, such as starvat\ldots
  \item[\textbf{\#2}] \texttt{[0.0036]} \textit{Spells/Freedom of Movement} -- \#\#\# Freedom of Movement  *4th-level abjuration*  **Casting Time:** 1 action  **R\ldots
  \item[\textbf{\#3}] \texttt{[-2.5567]} \textit{Gamemastering/Conditions} -- \#\# Restrained  - A restrained creature's speed becomes 0, and it can't benefit f\ldots
  \item[\textbf{\#4}] \texttt{[-3.8610]} \textit{Spells/Slow} -- \#\#\# Slow  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 120 \ldots
  \item[\textbf{\#5}] \texttt{[-4.3227]} \textit{Spells/Dominate Beast} -- \#\#\# Dominate Beast  *4th-level enchantment*  **Casting Time:** 1 action  **Range\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q16: Can you use Action Surge to cast two leveled spells in one turn?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} Based on the provided context, no, you cannot use Action Surge to cast two leveled spells in one turn. The Action Surge ability only allows you to take an additional action on top of your regular action, not an additional casting of a spell. Additionally, the Bonus Action spell casting rule states t\ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[3.4982]} \textit{Classes/Fighter} -- \#\#\# Action Surge  Starting at 2nd level, you can push yourself beyond your norma\ldots
  \item[\textbf{\#2}] \texttt{[2.1903]} \textit{Spells/# Spellcasting} -- \#\#\# Bonus Action  A spell cast with a bonus action is especially swift. You must\ldots
  \item[\textbf{\#3}] \texttt{[0.1570]} \textit{Spells/Compulsion} -- \#\#\# Compulsion  *4th-level enchantment*  **Casting Time:** 1 action  **Range:** \ldots
  \item[\textbf{\#4}] \texttt{[-1.7666]} \textit{Characterizations/Multiclassing} -- If you have more than one spellcasting class, this table might give you spell sl\ldots
  \item[\textbf{\#5}] \texttt{[-4.5305]} \textit{Spells/# Spellcasting} -- \# Combining Magical Effects  The effects of different spells add together while \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}
