\subsubsection*{\texttt{42-post-rerank-reorder}}
\label{app:samples:42_post_rerank_reorder}

\paragraph{Q3: How long does the Haste spell last?}
\noindent \textbf{Corr.:}~5.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} The Haste spell lasts for a duration of concentration, up to 1 minute.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[-1.1630]} \textit{Spells/Haste} -- \#\#\# Haste  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 30 \ldots
  \item[\textbf{\#2}] \texttt{[-4.3387]} \textit{Spells/Bestow Curse} -- \#\#\# Bestow Curse  *3rd-level necromancy*  **Casting Time:** 1 action  **Range:**\ldots
  \item[\textbf{\#3}] \texttt{[-4.8813]} \textit{Spells/Geas} -- \#\#\# Geas  *5th-level enchantment*  **Casting Time:** 1 minute  **Range:** 60 fee\ldots
  \item[\textbf{\#4}] \texttt{[-4.3627]} \textit{Spells/# Spellcasting} -- \#\# Duration  A spell's duration is the length of time the spell persists. A dura\ldots
  \item[\textbf{\#5}] \texttt{[-4.2668]} \textit{Spells/Modify Memory} -- \#\#\# Modify Memory  *5th-level enchantment*  **Casting Time:** 1 action  **Range:\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q5: Can a grappled creature cast spells?}
\noindent \textbf{Corr.:}~1.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} The context does not provide information on whether a grappled creature can cast spells or not. Therefore, I cannot find this in the provided rules.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[2.1648]} \textit{Spells/Arcane Hand} -- ***Grasping Hand***. The hand attempts to grapple a Huge or smaller creature wit\ldots
  \item[\textbf{\#2}] \texttt{[-1.5698]} \textit{Gameplay/Combat} -- \#\#\# Grappling  When you want to grab a creature or wrestle with it, you can use \ldots
  \item[\textbf{\#3}] \texttt{[-4.5285]} \textit{Spells/Confusion} -- \#\#\# Confusion  *4th-level enchantment*  **Casting Time:** 1 action  **Range:** 9\ldots
  \item[\textbf{\#4}] \texttt{[-3.3439]} \textit{Spells/# Spellcasting} -- \# Rituals  Certain spells have a special tag: ritual. Such a spell can be cast f\ldots
  \item[\textbf{\#5}] \texttt{[0.5121]} \textit{Gamemastering/Conditions} -- \#\# Grappled  - A grappled creature's speed becomes 0, and it can't benefit from \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q12: If a creature has exhaustion level 3 and is also restrained, what is its movement speed?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} I cannot find the rules in the provided context regarding a creature's movement speed when it has exhaustion level 3 and is also restrained. The context only mentions that exhaustion affects movement by reducing speed and that the Freedom of Movement spell can help a creature escape from nonmagical \ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.5239]} \textit{Gamemastering/Conditions} -- \#\# Exhaustion  Some special abilities and environmental hazards, such as starvat\ldots
  \item[\textbf{\#2}] \texttt{[-2.5567]} \textit{Gamemastering/Conditions} -- \#\# Restrained  - A restrained creature's speed becomes 0, and it can't benefit f\ldots
  \item[\textbf{\#3}] \texttt{[-4.3227]} \textit{Spells/Dominate Beast} -- \#\#\# Dominate Beast  *4th-level enchantment*  **Casting Time:** 1 action  **Range\ldots
  \item[\textbf{\#4}] \texttt{[-3.8610]} \textit{Spells/Slow} -- \#\#\# Slow  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 120 \ldots
  \item[\textbf{\#5}] \texttt{[0.0036]} \textit{Spells/Freedom of Movement} -- \#\#\# Freedom of Movement  *4th-level abjuration*  **Casting Time:** 1 action  **R\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q16: Can you use Action Surge to cast two leveled spells in one turn?}
\noindent \textbf{Corr.:}~1.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} No, you cannot use Action Surge to cast two leveled spells in one turn. With Action Surge, you gain an additional action, not an additional casting of a spell. You can use one of your actions to cast a spell and the other action granted by Action Surge for another action, such as attacking or using \ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[3.4982]} \textit{Classes/Fighter} -- \#\#\# Action Surge  Starting at 2nd level, you can push yourself beyond your norma\ldots
  \item[\textbf{\#2}] \texttt{[0.1570]} \textit{Spells/Compulsion} -- \#\#\# Compulsion  *4th-level enchantment*  **Casting Time:** 1 action  **Range:** \ldots
  \item[\textbf{\#3}] \texttt{[-4.5305]} \textit{Spells/# Spellcasting} -- \# Combining Magical Effects  The effects of different spells add together while \ldots
  \item[\textbf{\#4}] \texttt{[-1.7666]} \textit{Characterizations/Multiclassing} -- If you have more than one spellcasting class, this table might give you spell sl\ldots
  \item[\textbf{\#5}] \texttt{[2.1903]} \textit{Spells/# Spellcasting} -- \#\#\# Bonus Action  A spell cast with a bonus action is especially swift. You must\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}
