\subsubsection*{\texttt{50-transform-rewrite}}
\label{app:samples:50_transform_rewrite}

\paragraph{Q3: How long does the Haste spell last?}
\textit{Umgeschrieben:} What is the duration of the Haste spell in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~5.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} The duration of the Haste spell in DnD 5e is concentration, up to 1 minute.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Spells/Haste} -- \#\#\# Haste  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 30 \ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Spells/# Spellcasting} -- \#\# Duration  A spell's duration is the length of time the spell persists. A dura\ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Spells/Dominate Person} -- \#\#\# Dominate Person  *5th-level enchantment*  **Casting Time:** 1 action  **Rang\ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Spells/Geas} -- \#\#\# Geas  *5th-level enchantment*  **Casting Time:** 1 minute  **Range:** 60 fee\ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Spells/Compulsion} -- \#\#\# Compulsion  *4th-level enchantment*  **Casting Time:** 1 action  **Range:** \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q5: Can a grappled creature cast spells?}
\textit{Umgeschrieben:} Can a creature that is grappled cast spells in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~4.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} A creature that is grappled can still cast spells in DnD 5e, as long as it has the necessary components and focus if required by the spell. However, the Careful Spell metamagic ability described in the context does not apply to creatures that are grappled, as they are not "other creatures" that the \ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Classes/Sorcerer} -- \#\#\#\# Careful Spell  When you cast a spell that forces other creatures to make a \ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Gameplay/Combat} -- \#\#\# Grappling  When you want to grab a creature or wrestle with it, you can use \ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Gamemastering/Conditions} -- \#\# Grappled  - A grappled creature's speed becomes 0, and it can't benefit from \ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Spells/Arcane Hand} -- ***Grasping Hand***. The hand attempts to grapple a Huge or smaller creature wit\ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Gamemastering/Conditions} -- \#\# Paralyzed  - A paralyzed creature is incapacitated (see the condition) and ca\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q12: If a creature has exhaustion level 3 and is also restrained, what is its movement speed?}
\textit{Umgeschrieben:} What is the movement speed of a creature with exhaustion level 3 that is also restrained in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~4.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.50\\

\noindent\textbf{Antwort:} A creature with exhaustion level 3 has no movement speed due to the exhaustion condition. When a creature is restrained, its speed becomes 0, and it can't benefit from any bonus to its speed. Therefore, a creature with exhaustion level 3 that is also restrained has no movement speed in DnD 5e.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Gamemastering/Conditions} -- \#\# Restrained  - A restrained creature's speed becomes 0, and it can't benefit f\ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Spells/Slow} -- \#\#\# Slow  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 120 \ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Spells/Freedom of Movement} -- \#\#\# Freedom of Movement  *4th-level abjuration*  **Casting Time:** 1 action  **R\ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Spells/Dominate Person} -- \#\#\# Dominate Person  *5th-level enchantment*  **Casting Time:** 1 action  **Rang\ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Spells/Hold Monster} -- \#\#\# Hold Monster  *5th-level enchantment*  **Casting Time:** 1 action  **Range:*\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q16: Can you use Action Surge to cast two leveled spells in one turn?}
\textit{Umgeschrieben:} Can Action Surge be used to cast two leveled spells in a single turn in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} I cannot find this in the provided rules that Action Surge allows a Fighter to cast two leveled spells in a single turn. Action Surge only grants an additional action on top of the regular action and a possible bonus action. Casting a spell requires a separate action, so it is not possible to cast t\ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Classes/Fighter} -- \#\#\# Action Surge  Starting at 2nd level, you can push yourself beyond your norma\ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Spells/# Spellcasting} -- \#\#\# Bonus Action  A spell cast with a bonus action is especially swift. You must\ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Spells/Compulsion} -- \#\#\# Compulsion  *4th-level enchantment*  **Casting Time:** 1 action  **Range:** \ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Classes/Sorcerer} -- \#\#\#\# Quickened Spell  When you cast a spell that has a casting time of 1 action,\ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Characterizations/Multiclassing} -- If you have more than one spellcasting class, this table might give you spell sl\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}
