\subsubsection*{\texttt{80-mode-refine}}
\label{app:samples:80_mode_refine}

\paragraph{Q3: How long does the Haste spell last?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} The duration of the Haste spell is one minute. However, a druid or a ranger can use the Natural Recovery feature to extend the duration by 10 minutes each day for up to three uses. Additionally, a cleric or a paladin can use an action to extend the duration by one round. The Tome of Clear Thought do\ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Spells/Haste} -- \#\#\# Haste  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 30 \ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Spells/# Spellcasting} -- \#\# Duration  A spell's duration is the length of time the spell persists. A dura\ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Spells/Modify Memory} -- \#\#\# Modify Memory  *5th-level enchantment*  **Casting Time:** 1 action  **Range:\ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Spells/Geas} -- \#\#\# Geas  *5th-level enchantment*  **Casting Time:** 1 minute  **Range:** 60 fee\ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Treasure/Tome of Understanding} -- \#\#\# Tome of Understanding  *Wondrous item, very rare*  This book contains intuit\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q5: Can a grappled creature cast spells?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} A grappled creature's capacity to cast spells is contingent on the particular class or trait they possess. The details provided in the context don't offer clarification regarding this scenario.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Gameplay/Combat} -- \#\# Cast a Spell  Spellcasters such as wizards and clerics, as well as many monst\ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Monsters/# Monster Statistics} -- \#\#\# Innate Spellcasting  A monster with the innate ability to cast spells has th\ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Classes/Sorcerer} -- \#\#\#\# Careful Spell  When you cast a spell that forces other creatures to make a \ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Gameplay/Combat} -- \#\#\# Grappling  When you want to grab a creature or wrestle with it, you can use \ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Gamemastering/Conditions} -- \#\# Grappled  - A grappled creature's speed becomes 0, and it can't benefit from \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q12: If a creature has exhaustion level 3 and is also restrained, what is its movement speed?}
\noindent \textbf{Corr.:}~3.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.75\\

\noindent\textbf{Antwort:} With exhaustion level 3, the creature's movement speed is reduced. The specifics of the reduction aren't mentioned in the given context. If the creature is also restrained, it becomes immobile and its effective speed is 0.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Gamemastering/Conditions} -- \#\# Restrained  - A restrained creature's speed becomes 0, and it can't benefit f\ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Gameplay/Adventuring} -- \#\# Suffocating  A creature can hold its breath for a number of minutes equal to \ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Gamemastering/Conditions} -- \#\# Exhaustion  Some special abilities and environmental hazards, such as starvat\ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Spells/Freedom of Movement} -- \#\#\# Freedom of Movement  *4th-level abjuration*  **Casting Time:** 1 action  **R\ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Gamemastering/Conditions} -- \#\# Unconscious  - An unconscious creature is incapacitated (see the condition), \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q16: Can you use Action Surge to cast two leveled spells in one turn?}
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} Action Surge allows you to perform additional actions during your turn, but each action you take, including spellcasting actions, must adhere to the standard rules for casting spells. In this case, the Compulsion spell's duration and area of effect are not altered by casting it multiple times with A\ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0167]} \textit{Classes/Fighter} -- \#\#\# Action Surge  Starting at 2nd level, you can push yourself beyond your norma\ldots
  \item[\textbf{\#2}] \texttt{[0.0164]} \textit{Spells/# Spellcasting} -- \#\#\# Bonus Action  A spell cast with a bonus action is especially swift. You must\ldots
  \item[\textbf{\#3}] \texttt{[0.0161]} \textit{Classes/Sorcerer} -- \#\#\#\# Quickened Spell  When you cast a spell that has a casting time of 1 action,\ldots
  \item[\textbf{\#4}] \texttt{[0.0159]} \textit{Characterizations/Multiclassing} -- If you have more than one spellcasting class, this table might give you spell sl\ldots
  \item[\textbf{\#5}] \texttt{[0.0156]} \textit{Classes/Sorcerer} -- \#\#\#\# Flexible Casting  You can use your sorcery points to gain additional spell \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}
