\subsubsection*{\texttt{90-combined-best-guess}}
\label{app:samples:90_combined_best_guess}

\paragraph{Q3: How long does the Haste spell last?}
\textit{Umgeschrieben:} What is the duration of the Haste spell in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~5.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} The duration of the Haste spell in DnD 5e is concentration, up to 1 minute.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0667]} \textit{Spells/Haste} -- \#\#\# Haste  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 30 \ldots
  \item[\textbf{\#2}] \texttt{[0.0464]} \textit{Spells/Modify Memory} -- \#\#\# Modify Memory  *5th-level enchantment*  **Casting Time:** 1 action  **Range:\ldots
  \item[\textbf{\#3}] \texttt{[0.0323]} \textit{Spells/Geas} -- \#\#\# Geas  *5th-level enchantment*  **Casting Time:** 1 minute  **Range:** 60 fee\ldots
  \item[\textbf{\#4}] \texttt{[0.0323]} \textit{Spells/Dominate Person} -- \#\#\# Dominate Person  *5th-level enchantment*  **Casting Time:** 1 action  **Rang\ldots
  \item[\textbf{\#5}] \texttt{[0.0315]} \textit{Spells/# Spellcasting} -- \#\# Duration  A spell's duration is the length of time the spell persists. A dura\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q5: Can a grappled creature cast spells?}
\textit{Umgeschrieben:} Can a creature that is grappled cast spells in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~1.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} The context does not provide information on whether a grappled creature can cast spells or not. Therefore, I cannot find this in the provided rules.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0646]} \textit{Gamemastering/Conditions} -- \#\# Grappled  - A grappled creature's speed becomes 0, and it can't benefit from \ldots
  \item[\textbf{\#2}] \texttt{[0.0643]} \textit{Gameplay/Combat} -- \#\#\# Grappling  When you want to grab a creature or wrestle with it, you can use \ldots
  \item[\textbf{\#3}] \texttt{[0.0635]} \textit{Spells/Arcane Hand} -- ***Grasping Hand***. The hand attempts to grapple a Huge or smaller creature wit\ldots
  \item[\textbf{\#4}] \texttt{[0.0333]} \textit{Classes/Sorcerer} -- \#\#\#\# Careful Spell  When you cast a spell that forces other creatures to make a \ldots
  \item[\textbf{\#5}] \texttt{[0.0313]} \textit{Gameplay/Combat} -- \#\# Cast a Spell  Spellcasters such as wizards and clerics, as well as many monst\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q12: If a creature has exhaustion level 3 and is also restrained, what is its movement speed?}
\textit{Umgeschrieben:} What is the movement speed of a creature with exhaustion level 3 that is also restrained in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~4.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.62\\

\noindent\textbf{Antwort:} A creature with exhaustion level 3 has a speed of 0 due to the restrained condition. Therefore, its movement speed is not specified in the provided rules.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0630]} \textit{Gamemastering/Conditions} -- \#\# Restrained  - A restrained creature's speed becomes 0, and it can't benefit f\ldots
  \item[\textbf{\#2}] \texttt{[0.0489]} \textit{Spells/Freedom of Movement} -- \#\#\# Freedom of Movement  *4th-level abjuration*  **Casting Time:** 1 action  **R\ldots
  \item[\textbf{\#3}] \texttt{[0.0333]} \textit{Gamemastering/Conditions} -- \#\# Exhaustion  Some special abilities and environmental hazards, such as starvat\ldots
  \item[\textbf{\#4}] \texttt{[0.0323]} \textit{Spells/Slow} -- \#\#\# Slow  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 120 \ldots
  \item[\textbf{\#5}] \texttt{[0.0318]} \textit{Monsters/Wraith} -- \#\# Wraith  *Medium undead, neutral evil*  **Armor Class** 13  **Hit Points** 67 \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q16: Can you use Action Surge to cast two leveled spells in one turn?}
\textit{Umgeschrieben:} Can Action Surge be used to cast two leveled spells in a single turn in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~2.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} I cannot find this in the provided rules that Action Surge allows a Fighter to cast two leveled spells in a single turn. Action Surge only grants an additional action and a possible bonus action on the same turn. Spellcasting and Action Surge are separate mechanics in DnD 5e. The Quickened Spell met\ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0648]} \textit{Classes/Fighter} -- \#\#\# Action Surge  Starting at 2nd level, you can push yourself beyond your norma\ldots
  \item[\textbf{\#2}] \texttt{[0.0331]} \textit{Classes/Fighter} -- **Table- The Fighter**  | Level | Proficiency Bonus | Features                  \ldots
  \item[\textbf{\#3}] \texttt{[0.0325]} \textit{Spells/Heal} -- \#\#\# Heal  *6th-level evocation*  **Casting Time:** 1 action  **Range:** 60 feet \ldots
  \item[\textbf{\#4}] \texttt{[0.0306]} \textit{Spells/Confusion} -- \#\#\# Confusion  *4th-level enchantment*  **Casting Time:** 1 action  **Range:** 9\ldots
  \item[\textbf{\#5}] \texttt{[0.0167]} \textit{Spells/## Spell Lists (Wikilinked)} -- \#\#\#\# 5th Level  - [[Animate Objects]] - [[Cloudkill]] - [[Cone of Cold]] - [[Cre\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}
