\subsubsection*{\texttt{91-combined-sentwindow-best}}
\label{app:samples:91_combined_sentwindow_best}

\paragraph{Q3: How long does the Haste spell last?}
\textit{Umgeschrieben:} What is the duration of the Haste spell in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~5.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~1.00\\

\noindent\textbf{Antwort:} The duration of the Haste spell in DnD 5e is concentration, up to 1 minute.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0667]} \textit{Spells/Haste} -- \#\#\# Haste  *3rd-level transmutation*  **Casting Time:** 1 action  **Range:** 30 \ldots
  \item[\textbf{\#2}] \texttt{[0.0623]} \textit{Spells/Haste} -- Until the spell ends, the target's speed is doubled, it gains a +2 bonus to AC, \ldots
  \item[\textbf{\#3}] \texttt{[0.0328]} \textit{Spells/Haste} -- When the spell ends, the target can't move or take actions until after its next \ldots
  \item[\textbf{\#4}] \texttt{[0.0325]} \textit{Spells/Compulsion} -- \#\#\# Compulsion  *4th-level enchantment*  **Casting Time:** 1 action  **Range:** \ldots
  \item[\textbf{\#5}] \texttt{[0.0325]} \textit{Spells/Bestow Curse} -- If you use a spell slot of 5th level or higher, the duration is 8 hours.
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q5: Can a grappled creature cast spells?}
\textit{Umgeschrieben:} Can a creature that is grappled cast spells in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~4.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} A grappled creature can still cast spells in DnD 5e, as long as they have the necessary components and focus, and their hands are not restrained or otherwise incapable of performing the necessary gestures or material components. However, if the spell requires a ranged attack roll, the creature will \ldots

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0331]} \textit{Characterizations/Feats} -- - You can use your action to try to pin a creature grappled by you.
  \item[\textbf{\#2}] \texttt{[0.0331]} \textit{Spells/# Spellcasting} -- Remember that you have disadvantage on a ranged attack roll if you are within 5 \ldots
  \item[\textbf{\#3}] \texttt{[0.0323]} \textit{Spells/Arcane Hand} -- The hand attempts to grapple a Huge or smaller creature within 5 feet of it.
  \item[\textbf{\#4}] \texttt{[0.0321]} \textit{Monsters/Chain Devil (Devil)} -- An animated chain can grapple one creature of its own but can't make attacks whi\ldots
  \item[\textbf{\#5}] \texttt{[0.0315]} \textit{Gamemastering/Conditions} -- \#\# Grappled  - A grappled creature's speed becomes 0, and it can't benefit from \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q12: If a creature has exhaustion level 3 and is also restrained, what is its movement speed?}
\textit{Umgeschrieben:} What is the movement speed of a creature with exhaustion level 3 that is also restrained in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~5.00/5\quad \textbf{Faith.:}~1.00\quad \textbf{Relev.:}~1.00\quad \textbf{Ctx.Rel.:}~0.75\\

\noindent\textbf{Antwort:} The creature with exhaustion level 3 has its speed halved (Topic: Conditions, Table- Exhaustion Effects), and when restrained, its speed becomes 0 (Topic: Conditions, Restrained). Therefore, the movement speed of a creature with exhaustion level 3 that is also restrained is 0 in DnD 5e.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0641]} \textit{Gamemastering/Conditions} -- \#\# Restrained  - A restrained creature's speed becomes 0, and it can't benefit f\ldots
  \item[\textbf{\#2}] \texttt{[0.0469]} \textit{Classes/Barbarian} -- \#\#\# Fast Movement  Starting at 5th level, your speed increases by 10 feet while \ldots
  \item[\textbf{\#3}] \texttt{[0.0333]} \textit{Gamemastering/Conditions} -- **Table- Exhaustion Effects**  | Level | Effect                                 \ldots
  \item[\textbf{\#4}] \texttt{[0.0328]} \textit{Spells/Freedom of Movement} -- \#\#\# Freedom of Movement  *4th-level abjuration*  **Casting Time:** 1 action  **R\ldots
  \item[\textbf{\#5}] \texttt{[0.0328]} \textit{Spells/Freedom of Movement} -- For the duration, the target's movement is unaffected by difficult terrain, and \ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}

\paragraph{Q16: Can you use Action Surge to cast two leveled spells in one turn?}
\textit{Umgeschrieben:} Can Action Surge be used to cast two leveled spells in a single turn in DnD 5e?\\[2pt]
\noindent \textbf{Corr.:}~1.00/5\quad \textbf{Faith.:}~0.00\quad \textbf{Relev.:}~0.00\quad \textbf{Ctx.Rel.:}~0.25\\

\noindent\textbf{Antwort:} The Action Surge ability does not allow you to cast multiple leveled spells during the same turn using sorcery points or any other means as a Sorcerer.

\noindent\textbf{Abgerufene Chunks:}
\begin{itemize}[noitemsep, topsep=2pt]
  \item[\textbf{\#1}] \texttt{[0.0487]} \textit{Classes/Fighter} -- \#\#\# Action Surge  Starting at 2nd level, you can push yourself beyond your norma\ldots
  \item[\textbf{\#2}] \texttt{[0.0318]} \textit{Classes/Fighter} -- \#\#\#\# Hit Points  **Hit Dice:** 1d10 per fighter level  **Hit Points at 1st Level\ldots
  \item[\textbf{\#3}] \texttt{[0.0167]} \textit{Spells/# Spellcasting} -- You can't cast another spell during the same turn, except for a cantrip with a c\ldots
  \item[\textbf{\#4}] \texttt{[0.0167]} \textit{Spells/# Spellcasting} -- When you cast a spell with a casting time longer than a single action or reactio\ldots
  \item[\textbf{\#5}] \texttt{[0.0167]} \textit{Spells/## Spell Lists} -- \# SPELL LISTS  \#\# Bard Spells  \#\#\#\# Cantrips (0 Level)  - Dancing Lights - Light\ldots
\end{itemize}
\vspace{4pt}
\hrule
\vspace{6pt}
